On FX Rates and a Multivariate GARCH model

### 2016-10-03 papers/FX/fx.tex
some progress on the multivariate GARCH model.

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage[bookmarks=true]{hyperref}
\usepackage{bookmark}
\usepackage{graphicx}

@@

\subsection{IARCH(1)}
In this case $\alpha_{i, 1} = 1$, $\beta_{i, 1} = 0$. Thus, from the equation
\begin{equation*}
  \E (Z_i^2)^{\xi_i} = 1
\end{equation*}
we obtain $\xi_i = 1$. Suppose
\begin{eqnarray*}
  \E (Z_i^2 Z_j^2)^\xi &=& 1 \\
  (Z_i, Z_j) &\sim& N(0, \Sigma) \\
  \Sigma &=&
  \begin{pmatrix}
    1 & \rho \\
    \rho & 1
  \end{pmatrix}
\end{eqnarray*}
Re-writing the above equation gives
\begin{equation}
  \label{eq:iarch1_1st}
  {1 \over 2\pi}
  \int \int
  \left(
    \rho^2 x^4 + (1 - \rho^2) x^2 y^2 + 2 \rho \sqrt{1 - \rho^2} x^3 y
  \right)^\xi
  \exp\left(
    -{x^2 + y^2 \over 2}
  \right)
  dx dy = 1
\end{equation}
When $\rho = \pm 1$, it is clear $\xi = 1/2$. When $-1 < \rho < 1$,
we may re-write \eqref{eq:iarch1_1st} in polar coordinates to obtain
\begin{equation*}
  {1 \over 2\pi} \int_0^{\infty} r^{4\xi + 1} e^{-r^2 / 2} dr
  \int_{0}^{2\pi} \cos(\theta)^{2 \xi}
  \left(
    2 \rho^2 \cos(\theta)^2
    + 2 \rho \sqrt{1 - \rho^2} \cos(\theta) \sin(\theta) - \cos(\theta)^2 + 1 - \rho^2
  \right)^\xi d\theta = 1
\end{equation*}
Integrating the radial part of the integral results in
\begin{equation*}
  \int_{0}^{2\pi}
  \cos(\theta)^{2\xi}
  \left(
    2 \rho^2 \cos(\theta)^2 + \rho \sqrt{1 - \rho^2} \sin(2\theta) - \cos(\theta)^2 - \rho^2 + 1
  \right)^\xi d\theta
  = {2 \pi
    \over
    2^{2 \xi} \Gamma(2\xi + 1)
  }
\end{equation*}
After some manipulations we arrive at
\begin{equation}
  \label{eq:iarch_2nd}
  \int_{-1}^1 (\sin(\pi z) + \rho)^{2\xi} dz = {2 \over \Gamma(2\xi + 1)}
\end{equation}
Using this result, we immediately obtain for ARCH(1) models
\begin{equation*}
  \label{eq:arch_1st}
  \int_{-1}^1 (\sin(\pi z) + \rho)^{2\xi} dz =
  {2 \over \Gamma(2\xi + 1)}
  {1 \over (\alpha_{i, 1} \alpha_{j, 1})^\xi}
\end{equation*}

\section{General IGARCH(1)}
For general IGARCH(1) models, the equation
\begin{equation*}
  \E \left[
    (
    \alpha_{i,1} Z_1^2 + 1 - \alpha_{i,1}
    )^\xi
    (
    \alpha_{j,1} Z_2^2 + 1 - \alpha_{j,1}
    )^\xi\right] = 1
\end{equation*}
has to be solved numerically.
\section{Spectra of S\&P sectors}
\subsection{Utilities}
Fitting the daily returns' data of 25 companies that have been
included in the S\&P 500 index since 2010-01-01 and categorized in the
sector ``Utilities'', we obtained 23 GARCH(1, 1) models that satisfy
the condition
\begin{equation}
  \label{eq:garch_cond1}
  \alpha_1 + \beta_1 < 1  
\end{equation}
Then we simulate the GARCH(1, 1) processes with innovations having the
same covariance structure as those of the real data. Figure
\ref{fig:Utilities_eigenvalues} and \ref{fig:Utilities_eigenvectors1},
\ref{fig:Utilities_eigenvectors2}
compare the eigenvalues and eigenvectors, respectively, of the 
covariance matrices of the real and the simulated data.
\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.6]{Utilities_eigenvalues.pdf}
  \caption{Eigenvalues of Utilities: real \& simulated}
  \label{fig:Utilities_eigenvalues}
\end{figure}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage[bookmarks=true]{hyperref}
\usepackage{bookmark}
\usepackage{graphicx}
\usepackage{subfigure}

@@

\subsection{IARCH(1)}
In this case $\alpha_{i, 1} = 1$, $\beta_{i, 1} = 0$. Thus, from the equation
\begin{equation*}
  \E (Z_i^2)^{\xi_i} = 1
\end{equation*}
we obtain $\xi_i = 1$. Suppose
\begin{eqnarray*}
  \E (Z_i^2 Z_j^2)^\xi &=& 1 \\
  (Z_i, Z_j) &\sim& N(0, \Sigma) \\
  \Sigma &=&
  \begin{pmatrix}
    1 & \rho \\
    \rho & 1
  \end{pmatrix}
\end{eqnarray*}
Re-writing the above equation gives
\begin{equation}
  \label{eq:iarch1_1st}
  {1 \over 2\pi}
  \int \int
  \left(
    \rho^2 x^4 + (1 - \rho^2) x^2 y^2 + 2 \rho \sqrt{1 - \rho^2} x^3 y
  \right)^\xi
  \exp\left(
    -{x^2 + y^2 \over 2}
  \right)
  dx dy = 1
\end{equation}
When $\rho = \pm 1$, it is clear $\xi = 1/2$. When $-1 < \rho < 1$,
we may re-write \eqref{eq:iarch1_1st} in polar coordinates to obtain
\begin{equation*}
  {1 \over 2\pi} \int_0^{\infty} r^{4\xi + 1} e^{-r^2 / 2} dr
  \int_{0}^{2\pi} \cos(\theta)^{2 \xi}
  \left(
    2 \rho^2 \cos(\theta)^2
    + 2 \rho \sqrt{1 - \rho^2} \cos(\theta) \sin(\theta) - \cos(\theta)^2 + 1 - \rho^2
  \right)^\xi d\theta = 1
\end{equation*}
Integrating the radial part of the integral results in
\begin{equation*}
  \int_{0}^{2\pi}
  \cos(\theta)^{2\xi}
  \left(
    2 \rho^2 \cos(\theta)^2 + \rho \sqrt{1 - \rho^2} \sin(2\theta) - \cos(\theta)^2 - \rho^2 + 1
  \right)^\xi d\theta
  = {2 \pi
    \over
    2^{2 \xi} \Gamma(2\xi + 1)
  }
\end{equation*}
After some manipulations we arrive at
\begin{equation}
  \label{eq:iarch_2nd}
  \int_{-1}^1 (\sin(\pi z) + \rho)^{2\xi} dz = {2 \over \Gamma(2\xi + 1)}
\end{equation}
Using this result, we immediately obtain for ARCH(1) models
\begin{equation*}
  \label{eq:arch_1st}
  \int_{-1}^1 (\sin(\pi z) + \rho)^{2\xi} dz =
  {2 \over \Gamma(2\xi + 1)}
  {1 \over (\alpha_{i, 1} \alpha_{j, 1})^\xi}
\end{equation*}
Fitting ARCH(1) models to the FX return series and then simulating the
models produces a fairly good match between the spectra of the
simulated and the real series, as shown in figure
\ref{fig:FX_ARCH_eigenvalues} and \ref{fig:FX_ARCH_eigenvectors}.
\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.4]{FX_eigenvalues.pdf}  
  \caption{FX \& simulated ARCH eigenvalues}
  \label{fig:FX_ARCH_eigenvalues}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.3]{FX_eigenvectors}  
  \caption{FX \& ARCH eigenvectors}
  \label{fig:FX_ARCH_eigenvectors}
\end{figure}

\section{General IGARCH(1)}
For general IGARCH(1) models, the equation
\begin{equation*}
  \E \left[
    (
    \alpha_{i,1} Z_1^2 + 1 - \alpha_{i,1}
    )^\xi
    (
    \alpha_{j,1} Z_2^2 + 1 - \alpha_{j,1}
    )^\xi\right] = 1
\end{equation*}
has to be solved numerically. Figure \ref{fig:xi_rho0.5} shows $\xi$
as a function of $(\alpha_{i,1}, \alpha_{j,1})$ as defined by the
above equation.
\begin{figure}[htb!]
  \centering
  % \includegraphics[scale=0.4]{igarch_rho0dot5.pdf}
  \caption{$\xi(\alpha_1, \alpha_2)$ for $\rho = 1/2$}
  \label{fig:xi_rho0.5}
\end{figure}

\section{Spectra of S\&P sectors}
\subsection{Utilities}
Fitting the daily returns' data of 25 companies that have been
included in the S\&P 500 index since 2010-01-01 and categorized in the
sector ``Utilities'', we obtained 23 GARCH(1, 1) models that satisfy
the condition
\begin{equation}
  \label{eq:garch_cond1}
  \alpha_1 + \beta_1 < 1  
\end{equation}
Then we simulate the GARCH(1, 1) processes with innovations having the
same covariance structure as those of the real data. Figure
\ref{fig:Utilities_eigenvalues} and \ref{fig:Utilities_eigenvectors1},
\ref{fig:Utilities_eigenvectors2}
compare the eigenvalues and eigenvectors, respectively, of the 
covariance matrices of the real and the simulated data.
\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.6]{Utilities_eigenvalues.pdf}
  \caption{Eigenvalues of Utilities: real \& simulated}
  \label{fig:Utilities_eigenvalues}
\end{figure}
